---
title: "Subsetting lists in R"
author: "McEwen Khundi"
date: "08/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Examples of atomic vectors


```{r logic_vec}
logical_vec <- c(T,T,F,T,F,T,T)

#The vector
logical_vec

#Confirming atomic vectory type
class(logical_vec)
```

```{r integer_vec}
integer_vec <- c(1L,2L,3L,4L)

#The vector
integer_vec

#Confirming atomic vectory type
class(integer_vec)
```


```{r double_vec}
double_vec <- c(1.0,2.0,3.0,4.0)

#The vector
double_vec

#Confirming atomic vectory type
class(double_vec)
```

```{r character_vec}
character_vec <- c(1.0,2.0,3.0,4.0)

#The vector
character_vec

#Confirming atomic vectory type
class(character_vec)
```
## Examples of list vector

```{r list_vec}
list_vec <- list( logical_vec = logical_vec, integer_vec = integer_vec, double_vec = double_vec, character_vec = character_vec )

#The vector
list_vec

#Confirming list vectory type
---(list_vec)
```
## Choosing all members of a list

Subsetting lists(Choosing all members of a list)

```{r subseting_examp1}

# Example list
a = list(yb = c(1,2,3), d = "patient")

a

a[]
```
## Choosing all members of a list

Subsetting lists(Choosing all members of a list)

```{r subseting_examp2}

# Example list
a = list(yb = c(1,2,3), d = "patient")

a

a[]
```


Subsetting lists(Choosing list a that has member yb )

```{r subseting_examp3}

# Example list
a = list(yb = c(1,2,3), d = "patient")

a[1]

class(a[1])

a["yb"]
class(a["yb"])
```
Subsetting lists(Choosing vector yb from list a )

```{r subseting_examp4}

# Example list
a = list(yb = c(1,2,3), d = "patient")

a[[1]]
class(a[[1]])

a[["yb"]]
class(a[["yb"]])

a$yb
class(a$yb)

a$y
class(a$y)
```

Subsetting lists(Choosing vector yb from list a )

```{r subseting_examp5}

# Example list
a = list(yb = c(1,2,3), d = "patient")

a[[1]]
class(a[[1]])

a[["yb"]]
class(a[["yb"]])

a$yb
class(a$yb)

a$y
class(a$y)
```


Subsetting lists(Choosing members c(1,2))

```{r subseting_examp6}

# Example list
a = list(yb = c(1,2,3), d = "patient")

a[[1]][1:2]
class(a[[1]][1:2])

a[["yb"]][1:2]
class(a[["yb"]][1:2])

a$yb[1:2]
class(a$yb[1:2])

a$y
class(a$y[1:2])
```

## Your turn excercise
Subsetting lists(Choosing member “patient”)

```{r subseting_excercise}

# Example list
a = list(yb = c(1,2,3), d = "patient")

a[[2]]

-----

a[[--]]

----

a--

----
```
